Figures

### 2019-04-25 code/figures.rmd
Took the square root of tau2 to make figure 2 more informative

# Simulated data at various heterogeneity levels, prep for plotting
tau2_dist <- dens_tau2 %>%
 bind_rows(.id = "effect") %>%
 rename(Heterogeneity = tau_index) %>%
 mutate(Heterogeneity = recode(Heterogeneity,
                             '1' = "Zero",
                             '2' = "Small",
                             '3' = "Medium",
                             '4' = "Large"),
          Heterogeneity = as.factor(Heterogeneity))

# Observed tau22 estimates, i.e, results from main table, see table.rmd
# Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
observed_tau2 <- dat %>%
   split(.$effect) %>%
   map(transform_MA) %>% 
   map_dfr(summarizer, .id = "effect") %>%
   select(effect, tau2) %>%
   mutate(Heterogeneity = "Observed")

tau2_plot <- ggplot(tau2_dist, aes(x = tau2_hat, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed_tau2, aes(y = ..density.., x = tau2), bins = 200, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 0.05)) +
  scale_fill_brewer(palette = "Dark2",
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                         labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_color_brewer(palette = "Dark2",
                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                      labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
       legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

@@

#3) combine I2-tau2-density-plots----
densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
densities

>>>>

# Simulated data at various heterogeneity levels, prep for plotting
tau2_dist <- dens_tau2 %>%
 bind_rows(.id = "effect") %>%
 rename(Heterogeneity = tau_index) %>%
 mutate(Heterogeneity = recode(Heterogeneity,
                             '1' = "Zero",
                             '2' = "Small",
                             '3' = "Medium",
                             '4' = "Large"),
          Heterogeneity = as.factor(Heterogeneity),
        tau = sqrt(tau2_hat))

# Observed tau2 estimates, i.e, results from main table, see table.rmd
# Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
observed_tau <- dat %>%
   split(.$effect) %>%
   map(transform_MA) %>% 
   map_dfr(summarizer, .id = "effect") %>%
   select(effect, tau2) %>%
   mutate(Heterogeneity = "Observed",
          tau = sqrt(tau2))

tau_plot <- ggplot(tau2_dist, aes(x = tau, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed_tau, aes(y = ..density.., x = tau), bins = 130, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 0.25)) + #truncate plot for better visualization
  scale_fill_brewer(palette = "Dark2",
                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                     labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                         labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  scale_color_brewer(palette = "Dark2",
                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
                      labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
  theme(legend.position = c(0.85, 0.71),
       legend.background = element_rect(linetype = "solid", color = "black")) +
  scale_y_continuous(name = "Density") +
  scale_x_continuous(name = expression(paste(italic(tau)," estimate", sep = ""))) +
  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))

@@

#3) combine I2-tau2-density-plots----
densities <- plot_grid(I2_plot, tau_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
densities
